---
title: "My View"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    vertical_layout: scroll
   
   
runtime: shiny
---

```{r setup, include=FALSE}


library(flexdashboard)
library(flexdashboard)
library(tidyverse)
library(tidyquant)
library(plotly)
library(odbc)
library(RSQLite)
library(DBI)
library(RSQLite)
library(sqldf)
library(sqldf)
library(r2d3)
library(shiny)
library(htmltools)
library(DT)
library(rmarkdown)
library(viridis)
library(bannerCommenter)



```


# Cyber

```{r}

```

Column {data-height=1250, data-width=50}
------------------------------------------------------------------------
### Content

[Cyber attact types](#Cyber attact types)

```{r}

```

Column {data-height=1250, data-width=300}
------------------------------------------------------------------------
### Cyber attact types
```{r}
h1("Cyber attact types")
br()
HTML("<p>cyber attact types to html</p>")
```

###
```{r}

```



# bash/linux commands
```{r}

```
Column {data-height=1250, data-width=50}
---------------------------------------------------------------------------
### Content
[Basic Command](#Basic Command)
```{r}

```
Column {data-height=1250. data-width=300}
-------------------------------------------------------------------------------
### Basic Command
```{r}

```





# Python
```{r}

```
Column {data-height=1250, data-width=50}
------------------------------------------------------------------------

### Content

[EDA(Exploratory Data Analysis) and Data processing](#EDA(Exploratory Data Analysis) and Data processing)

[Graphic](#Graphic)

[Feature engineer](#Feature engineer)

[Models](#Models)

[Under and Over fit](#Under and Over fit)

[Hypotesis test](#Hypotesis test)

[Unit test](#Unit test)
```{r}

```

Column {data-height=1250, data-width=300}
-------------------------------------------------------------------------
### EDA(Exploratory Data Analysis) and Data processing
```{r}

```

### Graphic
```{r}

```

### Feature engineer
```{r}

```

### Models
```{r}

```

### Under and Over fit
```{r}

```
### Hypotesys test
```{r}

```
### Unit test
```{r}

```



# R
```{r}

```

Column {data-height=1250, data-width=50}
-----------------------------------------------------------------------
### Content
[Viridis](#Viridis)


[Code Chunks](#Code Chunks)

[Code Chunk2](#Code Chunk2)

```{r}

```



Column {data-height=1250, data-width=300}
-----------------------------------------------------------------------
### Viridis
This two color palette presented by this code which name is [viridis]\n
(http://github.com/sjmgarnier/viridis) packages. Each plot looks like\n
map of Maunga Whau volcano in Auckland, New Zealand.

```{r}
image(volcano, col = viridis(100))

image(volcano, col = viridis(100, option = "A"))

```


### Code Chunks
map of Maunga Whau volcano in Auckland, New Zealand.

```{r}
image(volcano, col = viridis(100))

image(volcano, col = viridis(100, option = "A"))
br()
```


### Code Chunk2
map of Maunga Whau volcano in Auckland, New Zealand.

```{r}
image(volcano, col = viridis(100))

image(volcano, col = viridis(100, option = "A"))
br()

```
img(Line2.png, Rd=False, alt="image")













